Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-28 ms.tex
added some more on specmatch results.

\begin{deluxetable*}{lcrrr}
\tablecaption{Observational estimates of the stellar parameters of KIC~12557548 from \citet{vanlieshout2016kic1255}}
\tablewidth{0pt}
\tablehead{
\colhead{Reference} &
\colhead{$ T_{eff,*} $} &
\colhead{$\log(g)$} &
\colhead{Evolutionary Status} &
\colhead{Method} \\
 & (K) & $\log$(cm s$^{-2}$) & & \\
 }
\startdata
  \citet{brown2011kic} & 4400 $\pm$ 200   & 4.6 $\pm$ 0.5    & main-sequence star & photometry \\
  \citet{rappaport}       & 4300 $\pm$ 250    &                            & main-sequence star & low-resolution spectroscopy \\
  \citet{kawahara2013starspots} & 4950 $\pm$ 70 & 3.9 $\pm$ 0.2 & sub-giant          & high-resolution spectroscopy \\
  \citet{huber2014kicprop} & 4550$^{+140}_{-131} $ & 4.622$^{+0.043}_{-0.036} $& main-sequence star & photometry \\
  This work - Specmatch	& 4500 	& 4.63	& main-sequence star & high-resolution spectroscopy\\
  This work - BOSZ		& 4500	& 4.5		& main-sequence star & high-resolution spectroscopy\\
\enddata
\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.}\label{tab:stellObsParams}
\end{deluxetable*}

@@

Figure \ref{fig:specMatch} shows the chi-squared differences between the median Subaru spectrum and the models.
The effective temperature radius show clear global $\chi^2$ minima for the HIRES spectral libraries.
The resulting best-fit parameters are T$_{eff}$=4500 K, [Fe/H]=-0.1$\pm$0.1, log(g)=4.5$\pm$0.1, R=0.7 $\pm$ 0.1 R$_\odot$.
We summarize these \texttt{specmatch} and BOSZ results in Table \ref{tab:stellObsParams}.

@@

>>>>

\begin{deluxetable*}{lcrrr}
\tablecaption{Observational estimates of the stellar parameters of KIC~12557548 from \citet{vanlieshout2016kic1255}}
\tablewidth{0pt}
\tablehead{
\colhead{Reference} &
\colhead{$ T_{eff,*} $} &
\colhead{$\log(g)$} &
\colhead{Evolutionary Status} &
\colhead{Method} \\
 & (K) & $\log$(cm s$^{-2}$) & & \\
 }
\startdata
  \citet{brown2011kic} & 4400 $\pm$ 200   & 4.6 $\pm$ 0.5    & main-sequence star & photometry \\
  \citet{rappaport}       & 4300 $\pm$ 250    &                            & main-sequence star & low-resolution spectroscopy \\
  \citet{kawahara2013starspots} & 4950 $\pm$ 70 & 3.9 $\pm$ 0.2 & sub-giant          & high-resolution spectroscopy \\
  \citet{huber2014kicprop} & 4550$^{+140}_{-131} $ & 4.622$^{+0.043}_{-0.036} $& main-sequence star & photometry \\
  This work - Specmatch	& 4500 $\pm$110 	& 4.63 $\pm$ 0.1 & main-sequence star & high-resolution spectroscopy\\
  This work - BOSZ		& 4500	& 4.5		& main-sequence star & high-resolution spectroscopy\\
\enddata
\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.}\label{tab:stellObsParams}
\end{deluxetable*}

@@

Figure \ref{fig:specMatch} shows the chi-squared differences between the median Subaru spectrum and the models.
The effective temperature radius show clear global $\chi^2$ minima for the HIRES spectral libraries.
The resulting best-fit parameters are T$_{eff}$=4500 K $\pm$ 110 K, [Fe/H]=-0.1$\pm$0.1, log(g)=4.5$\pm$0.1, R=0.7 $\pm$ 0.1 R$_\odot$.
We summarize these \texttt{specmatch} and BOSZ results in Table \ref{tab:stellObsParams}.

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.8\textwidth]{images/subaru/lincomb_kic1255.pdf}
\caption{Linear combination of templates that best matches KIC 1255.}\label{fig:specMatch}
\end{centering}
\end{figure*}
